---
title: "soc_anxiety_esm"
output: html_document
date: "2024-12-13"
output:
  html_document:
    toc: true
    toc_depth: '5'
    df_print: paged
  html_notebook:
    toc: true
    toc_float: true
    toc_depth: 5
    code_folding: hide
  word_document:
    toc: true
    toc_depth: '5'
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

```{css}

d-title {
    visibility: hidden;
  }
  
```

```{r, include = F,  warning=F, message=F}

options("scipen" = 100, "digits" = 4)

```

```{r, include = F,  include=F, warning=F, message=F}

library(tidyverse)
library(lme4)
library(corrplot)
library(lmerTest)
library(janitor)
library(lavaan)
library(semTools)
library(sjPlot)
library(lubridate)
library(patchwork)
library(ggstats)

```

# import data

```{r, include = F,  include=F}
big_data <- read.csv("data_processed/big_data.csv")
```

# working with the data

```{r, include = F}
#reversing "soc_esm_5_dolgok_vilagos_ertelme_celja" due to initial negative factor loading

big_data$soc_esm_5_dolgok_vilagos_ertelme_celja <- 8 - big_data$soc_esm_5_dolgok_vilagos_ertelme_celja

```


## creating model data

```{r, include = F}

model_soc <- 
  big_data %>% 
  select(id_esm, day_in_study, sex, age, contains(c("soc_esm", "szorongas", "depr", "mss_pos", "mss_neg", "mss_dis"))) %>% 
  group_by(id_esm, day_in_study) %>% 
  mutate(szorongas_mean = mean(szorongas, na.rm = T)) %>% 
  select(-szorongas) %>% 
  ungroup() %>% 
  distinct() 

```

## calculating ICC for soc items

```{r}

icc_loser             <- lmer(soc_esm_3_vesztesnek_erzem_magam ~ 1 + (1 | id_esm), data = model_soc)
icc_control           <- lmer(soc_esm_4_kontrollalhatatlan_erzelmek ~ 1 + (1 | id_esm), data = model_soc)
icc_meaning           <- lmer(soc_esm_5_dolgok_vilagos_ertelme_celja ~ 1 + (1 | id_esm), data = model_soc)
icc_meaningless       <- lmer(soc_esm_6_ertelmetlen_tevekenyseg ~ 1 + (1 | id_esm), data = model_soc)
icc_unfamiliar        <- lmer(soc_esm_ismeretlen_helyzet ~ 1 + (1 | id_esm), data = model_soc)
icc_disorder          <- lmer(soc_esm_zurzavaros_erzelmek ~ 1 + (1 | id_esm), data = model_soc)



tab_model(
  icc_loser,
  icc_control,
  icc_meaning,
  icc_meaningless,
  icc_unfamiliar,
  icc_disorder,
  
  show.ngroups = TRUE,  
  p.val = "satterthwaite", 
  show.aic = TRUE,
  show.aicc = TRUE,
  p.style = "stars",
  digits = 2, 
  digits.re = 3, 
  emph.p = TRUE,  
  string.ci = "95% CI",
  dv.labels = 
    c("icc_loser", 
      "icc_control", "icc_meaning",
      "icc_meaningless", "icc_unfamiliar",
      "icc_disorder"))


```

## plotting the distributions of conspiracy items within individuals

```{r, fig.width=8, fig.height=60}
#7188 rows removed?
model_soc %>% 
select(id_esm, contains("soc_esm")) %>%
pivot_longer(!id_esm, names_to = "soc_item", values_to = "values") %>%
ggplot(aes(values)) +
geom_bar() +
facet_grid(id_esm ~ soc_item)
```

# multilevel cfa of conspiracy items

```{r, include = F}
#### hierarchical factors

dat_cfa_soc <-
  model_soc %>% 
  select(id_esm, day_in_study, 
         soc_esm_3_vesztesnek_erzem_magam,
         soc_esm_4_kontrollalhatatlan_erzelmek,
         soc_esm_5_dolgok_vilagos_ertelme_celja,
         soc_esm_6_ertelmetlen_tevekenyseg,
         soc_esm_ismeretlen_helyzet, soc_esm_zurzavaros_erzelmek) %>%
  filter_at(vars(soc_esm_3_vesztesnek_erzem_magam:soc_esm_zurzavaros_erzelmek), all_vars(!is.na(.))) 
  

## covariance tests missing!
cfa_soc <- '

level: 1
      soc_within =~  
      soc_esm_3_vesztesnek_erzem_magam + soc_esm_4_kontrollalhatatlan_erzelmek +
      soc_esm_5_dolgok_vilagos_ertelme_celja + soc_esm_6_ertelmetlen_tevekenyseg +
      soc_esm_ismeretlen_helyzet + soc_esm_zurzavaros_erzelmek
      
      
level: 2
      soc_between =~  
      soc_esm_3_vesztesnek_erzem_magam + soc_esm_4_kontrollalhatatlan_erzelmek +
      soc_esm_5_dolgok_vilagos_ertelme_celja + soc_esm_6_ertelmetlen_tevekenyseg +
      soc_esm_ismeretlen_helyzet + soc_esm_zurzavaros_erzelmek
      
'

fit_soc <- cfa(model = cfa_soc, data = dat_cfa_soc, std.lv = TRUE, cluster = "id_esm", estimator = "ML")
```

```{r, include = F,  warning = T}

fitMeasures(fit_soc, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "srmr_within", "srmr_between"))
```

```{r, include = F}

summary(fit_soc, std = T)

```

```{r, include = F}

modificationindices(fit_soc) %>% arrange(-mi) #%>% view()

```

## factor loadings of the conspiracy items within and between individuals

```{r}
# within/betwwen-person factor loadings
# "soc_esm_5_dolgok_vilagos_ertelme_celja" reversed

(inspect(fit_soc, what = "std")$within$lambda)
(inspect(fit_soc, what = "std")$id_esm$lambda)

```

## reliability of soc factor within and between individuals

```{r}
# reliability
(semTools::reliability(fit_soc))

```

## adding the factor scores to the model data

```{r, include = F}
dat_soc_lev_2 <-
  dat_cfa_soc %>%
  select(id_esm) %>%
  distinct() %>%
  cbind(lavPredict(fit_soc, newdata = dat_cfa_soc[3:8], level = 2L))

dat_soc_lev_1 <-
  dat_cfa_soc %>%
  cbind(lavPredict(fit_soc, newdata = dat_cfa_soc[3:8], level = 1L)) %>%
  select(-contains("ESM_SOC"))

dat_soc <-
  dat_soc_lev_1 %>%
  left_join(dat_soc_lev_2, by = "id_esm") %>%
  mutate(soc_cfa =  soc_within + soc_between)

model_soc <-
  model_soc %>% 
  left_join(dat_soc, by = c("id_esm", "day_in_study"))

```

## adding lagged versions of anxiety and conspiracy to the model data

```{r, include = F}

model_soc_model <- 
  model_soc %>% 
  #select(id_esm, age, sex, day_in_study, szorongas_mean, soc_cfa, depr, mss_pos, mss_neg, mss_dis) %>%
  distinct() %>%
  group_by(id_esm) %>% 
  mutate(szorongas_mean_lag = lag(szorongas_mean),
         soc_cfa_lag = lag(soc_cfa),
         szorongas_mean_lag_centered = scale(szorongas_mean_lag, center = T, scale = F),
         soc_cfa_lag_centered = scale(soc_cfa_lag, center = T, scale = F))

```

# model 1: predicting soc from lagged anxiety

```{r}
model_1 <- 
  lmer(soc_cfa ~ age + sex + day_in_study + 
         szorongas_mean_lag_centered + soc_cfa_lag + 
         (szorongas_mean_lag_centered + soc_cfa_lag | id_esm), data = model_soc_model)

summary(model_1)
```


```{r}
plot_model(model_1, type = "std")
tab_model(model_1, show.std = T, show.aic = T)

```

# model 2: predicting anxiety from lagged soc

```{r}
model_2 <- 
  lmer(szorongas_mean ~ age + sex + day_in_study + 
         szorongas_mean_lag_centered + soc_cfa_lag + 
         (szorongas_mean_lag_centered + soc_cfa_lag | id_esm),
       data = model_soc_model)


summary(model_2)
```


```{r}
plot_model(model_2, type = "std")
tab_model(model_2, show.std = T, show.aic = T)

```